No amount of acknowledgement would be enough to express the gratitude I feel for you, Professor Rao. Your presence has not only helped me do scientific research, but has vastly shaped me as a person. My deepest regards to you are for not only being my Thesis supervisor to the truest of terms, but for performing duties well beyond the call of that; for being my best critic; and for being the prime example of someone you think worth becoming. I am one of those luckiest graduate students born on this planet.

I am deeply indebted to Professor Dipankar Bhattacharya, not only for excellent academic suggestions, advice, and support, but also for showing what diligence and effective communication can achieve; you are a master of many arts, achieving even a fraction of which is a lot for young researchers like me. Thank you for being such a massive inspiration.

I would like to express my deep gratitude to many people who have helped me at different stages of my TIFR journey: my batchmates Sounak and Sarbajaya for helping me survive graduate course work; my previous flatmates Gowtham and Aditya for being such nice human beings and friends in need; Joe Philip Ninan, for being a friend, an amazing senior, an excellent teacher of the tricks of the trade, and a source of great inspiration; senior Jishnu Bhattacharya for great advice as well as helping me with many technical details; Professor Rajdeep Sensarma for being an excellent teacher; Professors Rishi Sharma and Basudeb Dasgupta for guiding me at a crucial stage; and Professors D K Ojha and H M Antia for departmental support. This Thesis would not have been possible without either of you.

My sincere thanks to Professor Andrzej A Zdziarski for amazing scientific leadership, and warm hospitality at NCAC, Warsaw. I would like to thank all the members of the \AS -CZTI collaboration, but especially Rakesh Khanna, Mithun NPS, and Ajay Vibhute, for helping me integrate smoothly into the collaboration and with data and pipeline related queries throughout; and Vidushi Sharma for various updates about detected GRBs. My deepest gratitude is for all members of the staff of the TIFR canteens and Jagadish canteen, as well as the doctors and staff of the TIFR Medical Section, for their constant services that ensured an easy life in the campus.

I have deep regards for those who showed me the world of mountains, and those with whom I continue to share the love for this world -- a good fraction of these years has been spent in your lovely company. Naming you all is a mountain that I would rather not attempt to climb! I would like to thank my friends: Susmita for moral support during challenging times, and Jyotirmoy for being such a lovely person to be around with.

The last few months have been the toughest, but would have been worse without your timely intervention and excellent guidance: Nandini, I owe a lot to your hand of friendship, without which reaching the stage of completion would not have been a reality. I sincerely thank my psychotherapist Dr Priyanka Raut for digging me out of the pit that I was stuck in. I express my gratitude to Professor Sourav Chatterjee, for being a friend rather than a colleague: academia needs more people like you who takes mental health and depression seriously, and lends a hand of support during testing times.

None of the research I did would have been possible without the great works of the coders of the Free Software Foundation, to whom I express my most sincere gratitude. I would like to thank the Government of India and the people of this nation for funding my research.

Finally and most importantly, I express my sincere thanks to my parents, for believing in my dreams.